---
title: "Quiz P4DS-PS"
author: "Team Algoritma"
date: "6/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This quiz is part of Algoritma Academy assessment process. Congratulations on completing the Programming for Data Science and Practical Statistics course! We will conduct an assessment quiz to test the practical programming techniques that you have learned from the course. The quiz is expected to be taken in the classroom, please contact our team of instructors if you missed the chance to take it in class.

# Instruction

In this quiz, we will be using a retail dataset. You can get the CSV file stored within the `datainput` folder under the `retail.csv` file. The data stored a record of a transactions of a retail store specifying several variables. Please take a look at the following glossary for your reference:

- `Order.ID`: Id of order.
- `Order.Date`: Date of order.
- `Ship.Date`: Date of shipment.
- `Ship.Mode`: Type of shipment.
- `Customer.ID`: Id of customer.
- `Segment` : Customer's segment.
- `Product.ID`: Id of product.
- `Category` : Product category with 3 levels ("Furniture", "Office Supplies", "Technology")
- `Sub.Category`: more specific product category
- `Product.Name`: Name of product that was sold.
- `Sales`: How much earning from each sale.
- `Quantity`: Quantity of item sold.
- `Discount`: How much discount was given for each sale.
- `Profit`: How much can a company earn from each sale.

```{r}
# read the data here and inspect the data
retail <- read.csv("datainput/retail.csv")
head(retail)
```


We will split this quiz into 2 main sections: Programming for Data Science and Practical Statistics, each assessing the respective knowledge we have learned in the 2 courses.

## Programming for Data Science

1. Among the records, there were several transactions that were sold with a quantity of more than 5. However, we are more interested in finding out how many transactions that generate above-average profit but were sold with a quantity of lesser than 5. Use a conditional subsetting to find out the number of transactions with the given conditions!
  - [v] 1380
  - [ ] 1793
  - [ ] 2551
  - [ ] 758
  
```{r}
# code here
retail_clean <- retail[ , -c(1,2,3,4,5,6,7,8,9,10,11,13)]
retail_clean
```
```{r}
retail_clean$Profit <- as.integer(retail_clean$Profit)
summary(retail_clean)
```
```{r}
retail_untung <- retail_clean[retail_clean$Profit >= 28.34 & retail_clean$Quantity < 5, ]
nrow(retail_untung)
```

2. If you take a look at the `Ship.Mode` column, you will see there are several types of shipping mode. Among all customer segments, which segment made up most of the first-class shipment?
  - [v] Consumer
  - [ ] Corporate
  - [ ] Home Office
  
```{r}
# code here
retail_clean <- retail[ , -c(1,2,3,5,7,8,9,10,11,12,13,14)]
  table(retail_clean$Ship.Mode, retail_clean$Segment)
```


3. If we are to analyze the subcategories within the Office Supplies category, which are the 3 most popular subcategories, taking into account the total quantity of the item sold from each subcategory?
  - [v] Binder, Paper, Storage
  - [ ] Appliances, Art, Binder
  - [ ] Supplies, Envelopes, Fasteners
  - [ ] Paper, Binder, Art
  
```{r}
# code here
retail_clean1 <- retail[ , -c(1,2,3,4,5,6,7,8,10,11,12,13,14)]
a <- table(retail_clean1)
a

```


## Practical Statistics

4. In descriptive statistics, there are two main measurements that are commonly used to describe data distribution: central tendency and measure of spread. Which statistical measure can be used to describe the latter one?
  - [ ] Probability
  - [ ] Mean
  - [v] Standard Deviation
  - [ ] Correlation

5. Find out the correlation between Sales and Profit of the transactions using the `cor()` function. Based on the correlation between the two, which of the following statements are true?
  - [v] As the Sales increase, the Profit gained decreases
  - [ ] As the Sales decreases, the Profit gained decreases
  - [ ] As the Sales increase, the Profit is fixed
  
```{r}
# code here
retail
cor(retail$Sales,retail$Profit)
plot(retail$Sales,retail$Profit)
```


6. Consider this case: The retail company would like to apply a promotion to increase the number of sales. Based on historical records, you know that the monthly sales population has an average of 47,858.35 with a standard deviation of 25,195 and is distributed normally. After the promotion applied for a month, the company gained a total sales of 81,777. Using 95% confidence interval, perform a significance test using z-test to find out whether the promotion managed to significantly affect the number of sales. How would you conclude the test using the given information?
  - [v] Fail to reject the null hypothesis, the promo does not have a statistically significant impact
  - [ ] Fail to reject the null hypothesis, the promo has a statistically significant impact
  - [ ] Reject the null hypothesis, the promo has a statistically significant impact
  - [ ] Reject the null hypothesis, the promo does not have a statistically significant impact

I. Hypothesis
H0: Sales = 47858.35 (promotion does not affect number of sales)
H1: Sales > 47858.35 (promotion does affect number of sales)

II. Statistic

```{r}
# code Here
b <- pnorm(q = 81777, mean = 47858.35, sd = 25195, lower.tail = T)
1-b
```
